Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-26 manuscript/climate_sensitivity_draft.Rmd
Updated SI table and figure names

### Supplementary Information

**NEED TO UPDATE !!****
Table S1. Monthly Palmer Drought Severity Index (PDSI), and its rank among all years between 1950 and 2009 (driest=1), for focal droughts.

@@

Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.

Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.

Figure S1. Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to each focal drought

Figure S2. Map of ForestGEO plot showing topographic wetness index and location of cored trees

@@

Figure S6. Visualization of best model, with data, for all droughts combined.

>>>>

### Supplementary Information
Table S1. Monthly Palmer Drought Severity Index (PDSI), and its rank among all years between 1950 and 2009 for focal droughts.

@@

Table S6. Individual tests of species traits as drivers of drought recovery ($Rc$).

Table S7. Individual tests of species traits as drivers of drought resilience ($Rs$).

Table S8. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.

Table S9. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.

Table S10. Summary of top models for each drought instance, where $Rc$ is used as the response variable.

Table S11. Summary of top models for each drought instance, where $Rs$ is used as the response variable.

Figure S1. Time series of Palmer Drought Severity Index (PDSI) for the 2 years prior and after each focal drought.

Figure S2. Map of ForestGEO plot showing topographic wetness index and location of cored trees.

@@

Figure S6. Density plot of Recovery ($Rc$) values for each focal year.

Figure S7. Drought recovery, $Rc$, across species for the three focal droughts.
